Alex's Notes and Text Fragments for the JSS Manuscript

### 2022-05-24 paper/article.Rmd

@@

### Spatial leave-one-out with buffer

@@

### Leave-one-disc-out with optional buffer

@@

### Clustering-based: using coordinates

@@

### Geometric: using rectangular blocks

@@

<!-- FIXME: -->
### Custom: "customcv" in \pkg{mlr3} {short-title="Custom: customcv in mlr3" #sec:custom-cv}
<!-- {#sec:custom-cv} -->
<!-- \subsubsection[Custom: \code{"customcv"} in mlr3]{Custom: \code{"custom\_cv"} in \pkg{mlr3}} -->

@@

### Geometric: using rectangular blocks

@@

<!-- FIXME: underscore missing -->
###  Custom: "cv" with grouping in \pkg{mlr3} {short-title="Custom cv with grouping in mlr3" #sec:custom-cv-grouping}

@@

### Clustering: using feature-based clustering

@@

#### CV at the time-point level: "leave-time-out" (LTO)

@@

#### CV at the location level: "leave-location-out" (LLO)

@@

#### "Leave-location-and-time-out" (LLTO)

>>>>

  \usepackage{underscore}

@@

### Spatial leave-one-out with buffer --- \code{"spcv_buffer"} {short-title='Spatial leave-one-out with buffer --- "spcv_buffer"' }

@@

### Leave-one-disc-out with optional buffer --- \code{"spcv_disc"} {short-title='Leave-one-disc-out with optional buffer --- "spcv_disc"' }

@@

### Clustering-based: using coordinates --- \code{"spcv_coords"} {short-title='Clustering-based: using coordinates --- "spcv_coords"' }

@@

### Geometric: using rectangular blocks --- \code{"spcv_tiles"} {short-title='Geometric: using rectangular blocks --- "spcv_tiles"' }

@@

### Custom: `"custom_cv"` in \pkg{mlr3} {short-title='Custom: "custom_cv" in mlr3' #sec:custom-cv}

@@

### Geometric: using rectangular blocks --- \code{"spcv_block"} {short-title='Geometric: using rectangular blocks --- "spcv_block"' }

@@

###  Custom: `"cv"` with grouping in \pkg{mlr3} {short-title='Custom: "cv" with grouping in mlr3' #sec:custom-cv-grouping}

@@

### Clustering: using feature-based clustering --- \code{"spcv_env"} {short-title='Clustering: using feature-based clustering --- "spcv_env"' }

@@

#### CV at the time-point level: "leave-time-out" (LTO) --- \code{"sptcv_cstf"} {short-title='CV at the time-point level: "leave-time-out" (LTO) --- "sptcv_cstf"' }

@@

#### CV at the location level: "leave-location-out" (LLO) --- \code{"sptcv_cstf"} {short-title='CV at the location level: "leave-location-out" (LLO) --- "sptcv_cstf"' }

@@

#### "Leave-location-and-time-out" (LLTO) --- \code{"sptcv_cstf"} {short-title='"Leave-location-and-time-out" (LLTO) --- "sptcv_cstf"' }
